Collision rates of planetesimals near mean-motion resonances

### 2020-11-12 main.tex
Move libration timescale calculation to section 2, add calculation of gas damping on orbits of planetesimals

@@

\textbf{Move libration timescale here?}

@@

\textbf{Consider moving libration timescale to section \ref{sec:dynamics}.} All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
\begin{equation}\label{eq:lib_time}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
\end{equation}

@@

To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly 
coupled to the gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
\citep{1976PThPh..56.1756A}

>>>>

\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit sinusoidal oscillations. In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}

\begin{equation}\label{eq:lib_time}
	\omega_{0} = 3 p^{2} C_{r} n e^{\left| -q \right|}.
\end{equation}

\noindent \textbf{For the most prominent interior mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}

@@

\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of the planetesimals. For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}}

\textbf{\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 au, the gaseous component of the solar nebula has a density of $4 
\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
density of 2 g cm$^{-3}$ and an eccentricity of 0.1, the damping timescale is on the order of $10^{5}$ years. This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale. For this reason, we do not model the effects of gas drag, although we consider its effects when constructing initial conditions for our simulations, which is discussed next.}

@@

\textbf{Consider moving libration timescale to section \ref{sec:dynamics}.} All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. \textbf{TODO: Remove this, discussion of libration timescale has been moved to section \ref{sec:dynamics}}. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
\begin{equation}\label{eq:lib_time_old}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
\end{equation}

@@

To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly 
coupled to the gas. \textbf{TODO: Shorten this a bit, since we introduce this timescale in section \ref{sec:dynamics}.} For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
\citep{1976PThPh..56.1756A}
